The Lipid Interactome Repository

### 2025-02-26 LipidProbe/Sphinganine.qmd
Berit made us new structure figures, new text in data background section
minor changes to study info

---
title: "Trifunctional sphinganine"
prefer-html: true
format: html
---

@@

:::{.border}
![](/LipidProbe/Structures/SphinganineStructure.png)
:::

@@

## Gene Ontology enrichment

@@

>>>>

---
title: "Trifunctional Sphinganine"
prefer-html: true
format: html
---

@@

:::{.border}
![Trifunctional Sphinganine](/LipidProbe/Structures/TF_Sphinganine.png)
:::

@@

## Gene Ontology Analysis

@@

[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)

### 2025-02-26 StudyInformation_includes/SF_2024_A_include.qmd
minor changes to study info

@@

>>>>

<a href="/LipidProbe/Sphingosine.qmd" class="hover-preview">Trifunctional Sphingosine</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_Sphingosine.png" alt="Trifunctional Sphingosine" />
</span>

<a href="/LipidProbe/Sphinganine.qmd" class="hover-preview">Trifunctional Sphinganine</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_Sphinganine.png" alt="Trifunctional Sphinganine" />
</span>

@@

#### Uncaging & Crosslinking timeline

| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
|:-------|:------:|:------:|:------:|:------:|
| Sph    | 60 min | 5 min  | 15 min | 5 min  |
| Spa    | 60 min | 5 min  | 15 min | 5 min  |

### 2025-02-26 StudyInformation_includes/SF_2024_B_include.qmd
updating with includes structure
minor changes to study info

## Study details

#### Authors
Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz

#### Journal
ACS Chemical Biology

<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}

#### Abstract

@@

#### Lipid probes utilized

#### Cell line analyzed

@@

#### Mass spectrometry quantification method

@@

#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

>>>>

#### Study details

##### Authors
Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz

##### Journal
ACS Chemical Biology

<https://doi.org/10.1039/D4CC00974F>{target="_blank"}

##### Abstract

@@

##### Lipid probes utilized

<a href="/LipidProbe/1-10_FattyAcid.qmd" class="hover-preview">Trifunctional 1-10 Fatty Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_1-10_fatty_acid.png" alt="Trifunctional 1-10 Fatty Acid" />
</span>

<a href="/LipidProbe/8-3_FattyAcid.qmd" class="hover-preview">Trifunctional 8-3 Fatty Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_8-3_fatty_acid.png" alt="Trifunctional 8-3 Fatty Acide" />
</span>

##### Cell line analyzed

@@

#### Uncaging & Crosslinking timeline

| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
|:-------|:------:|:------:|:------:|:------:|
| 1-10 FA|  min |  min  |  min |  min  |
| 8-3 FA |  min |  min  |  min |  min  |

##### Mass spectrometry quantification method

@@

##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
